WordRec Experiment

### 2019-01-31 Analysis/process.Rmd
specify sample size for adult data
modif exp adults
second version cogsci

@@

d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
  filter(type == "Test") %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ block)+

@@

fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.04), lower=c(0,0), algorithm="port")

@@

ggplot(model_data_plot, 
#ggplot(subset(model_data_plot, group=='children'),
      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
  #geom_point()+
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                 position = position_dodge(width = .1),
                 size=0.2) + 
  geom_line() + 
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) + facet_grid(group~key, scales="free_y") +
  theme(aspect.ratio = 0.7)

>>>>

Sample size:
The following are the analysese done with adult pilot data.
We plan to collect data from 60 participants on Amazaon MTurk.

@@

#The following is a test with adult pilot data
d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
#d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
  filter(type == "Test", #Here I will  filter out particiapants whose first language is arabic or hindi
         other != "yes") %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ block)

@@

fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.1), lower=c(0,0), algorithm="port")

@@

ggplot(subset(model_data_plot, key == "human"), 
      aes(x = sound_dist, y = value, 
          group = factor(concept_dist), 
          col = factor(concept_dist)
          )) +
  #geom_point()+
  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
                 position = position_dodge(width = .1),
                 size=0.2) + 
  geom_line() + 
  geom_line(data=subset(model_data_plot, key == "prediction_2"), linetype=2, size=0.5, col='black')+
  geom_point(data=subset(model_data_plot, key == "prediction_2"), size=1, col='black')+
  geom_hline(yintercept = 0.50, linetype="dashed") +
  xlab("Auditory similary") +ylab("Accuracy")+
  scale_colour_discrete(name="Visual similarity")+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) + facet_grid(.~group) +
  theme(aspect.ratio = 0.7)
